Beyond Adaptive Web Design

### 2014-02-19 paper/paper.tex
refactor(): rewrite Abstract

\begin{abstract}
Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also new kinds of internet connection. But there are not just smartphones and desktop computers. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more. So it is necessary to adapt web pages for different devices and new interaction methods. In our work, we follow Mobile First and Progressive Enhancement design, which emphasises a great performance on mobile devices and later profit on high-end computers. We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation. The evaluation of the proposed method of adaptation shows slightly better results than original approach.
\end{abstract}

@@

Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more. We also have many types of internet connections with different qualities.

>>>>

\begin{abstract}
Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also high-latency networks. But there are not just smartphones and desktop computers. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. So it is necessary to adapt web pages for different devices and new interaction methods. Several new methods for designing web are rapidly evolving. We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation.
\end{abstract}

@@

Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. We also have many types of internet connections with different qualities.
